### 2017-09-26 TF-vldb2018/sec-appendix.tex

\revise{
The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

@@

>>>>

The decision version of the {\em pattern fragmentation} problem, denoted by $\kw{dOFGP}(P, h, r_1, r_2)$,
is to decide whether there exists a fragmentation \{${P}_{f1}$, \ldots, $P_{fh}$, $C$\} such that,
(a) $\max_i |P_{fi}| \leq r_1\cdot\frac{|P|}{h}$ and (b) $|C|\leq r_2|P|$.

@@

\revise{
\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

@@

\eat{%%%% Wrong proof %%%
\vspace{-2.5ex}
\etitle{Lower bound.}
We next show that it is \NP-hard to determine whether there exists an $h$-fragmentation and remains \NP-hard even when $h$ = 2,
by reduction from the {\em minimum cut} problem, which is known \NP-complete\footnote{\small http://www.nada.kth.se/$\sim$viggo/wwwcompendium/node85.html}.

\vspace{-2ex}
Given an instance of the minimum cut problem,
we construct an instance of $h$-fragmentation problem.
It can be achieved by taking $H$ as $P$, and setting $h=2$, $r_1=h$ and $r_2 = m/|P|$.
Indeed, the minimum cut problem is a special case of the of $h$-fragmentation problem.
}%%EAT
